The \dealii Library, Version 9.4

### 2022-06-24 9.4/paper.tex
Added boost.

@@

\dealii version 9.4.0 was released June 10, 2022.
\todo{Update release date.}
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.4. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Experimental integration of the Computational Geometry Algorithms Library (CGAL) (see Section~\ref{sec:cgalwrappers});
  \item Performance improvements in the particle infrastructure (see Section~\ref{sec:particles});
  \item Improvements to unstructured communication (see Section~\ref{sec:CA});
  \item Three new tutorial programs and one new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class interpolates values defined on one
  triangulation onto a second potentially unrelated triangulation.
  By using this class, one can output the result obtained on an
  unstructured mesh on a structured one (which might facilitate a more
  memory-efficient storage format, for example if this second
  triangulation is a uniformly refined rectangle or box), or one can create a slice in 3D.
  \item The new member function \texttt{find\_point\_owner\_rank()} of
        \texttt{parallel\allowbreak ::distributed::\allowbreak Tri\allowbreak angulation} allows one to find the MPI
  ranks of cells containing specified points.
  It is communication-free and leverages the functionality of \pfrst (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. This information will
  enable efficient construction of the
  communication pattern used in the class \texttt{Utilties::\allowbreak MPI::\allowbreak RemotePointEvaluation}. Furthermore, this function could be used in the future to allow
  particle simulations in which particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction()}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description is applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \item A new DoF renumbering function \texttt{DoFRenumbering::support\_point\_wise()} which groups together
  shape functions by their support point. This functionality is useful in both developing nodal schemes since, e.g., the $x$, $y$, and $z$
  velocities at a point will be consecutive in the solution vector. It also improves interoperability with external libraries which expect
  data in this format.
  \item A new module \texttt{Utilities::MPI::LargeCount} which enables sending and receiving MPI messages containing more than $2^{31}$ objects.
  This library either uses the new MPI-4 functions, such as \texttt{MPI\_Send\_c()}, or an internal implementation of large objects for
  compatibility with MPI-3.
  \item The \texttt{FEInterfaceValues} class, which computes common quantities at the interface of two cells, has been overhauled to make it
  more consistent with the rest of the library and use more intuitive names for functions. For example,
  \texttt{FEInterfaceValues::jump\_gradient()} is now \texttt{FEInterfaceValues::jump\_in\_shape\_gradients()}. Several new
  functions, such as \texttt{FEInterfaceValues::get\_jump\_in\_function\_values()}, have also been added.
  \item Vectors attached to \texttt{DataOut} do not need to be in ghosted state anymore. Internally, we create a copy of the vector with appropriate ghosting.
\end{itemize}
%
The changelog lists more than 100 other features and bugfixes.

@@

Specifically, the following are the key new classes and functions:
\begin{itemize}
  \item The \texttt{MeshClassifier} class identifies how the active cells and faces are located relative to the zero contour of the level set function, as illustrated in Figure~\ref{fig:location-to-level-set}. Its member function \texttt{location\_to\_level\_set()} takes a cell or face and
        returns an enum, \texttt{LocationToLevelSet}, with values \{\texttt{inside}, \texttt{outside}, \texttt{intersected}\}.
        This information is typically needed when choosing what element a cell of the \texttt{DoFHandler} should use.

@@

The Computational Geometry Algorithms Library (CGAL, \url{https://www.cgal.org/}) is a widely used
library to describe geometries and meshes \cite{cgal}. \dealii now
has wrappers for CGAL classes and functions, provided in the new
namespace \texttt{CGALWrappers}, and implementing functionality
spanning from mesh generation to boolean operations between \dealii
triangulations and cells. These wrappers are enabled only if \dealii
is compiled with \texttt{C++17}. \textit{Note: This feature is still experimental and
interfaces might change during the next release cycle.}

@@

A related function is
\texttt{GridGenerator::surface\_mesh\_to\_volumetric\_mesh()}, which
computes a tetrahedral volume triangulation \texttt{Triangulation<3>}, based on a
given surface triangulation \texttt{Triangulation<2,3>} that bounds
the three dimensional shape.

CGAL also provides Boolean operations on meshes, as available in the
utility function
\texttt{CGALWrappers::\allowbreak{}compute\_boolean\_operation()}. The
available operations are \textit{co-refinement}, \textit{intersection},
\textit{union}, and \textit{difference}. Oftentimes, boolean
operations and co-refinement around the intersection produces
badly shaped mesh cells. To overcome this issue, one can use \texttt{CGALWrappers::\allowbreak{}remesh\_surface()}. Figure~\ref{fig:corefinement_remeshed} shows a graphical example.
A possible workflow is the following:
\begin{c++}
// 1) create deal.II triangulations, e.g., cube and sphere (not shown)  
Triangulation<spacedim> tria0, tria1;

@@

// 5) convert surface to volume mesh via surface_mesh_to_volumetric_mesh()
\end{c++}
The output of the boolean operation can be seen in Fig.~\ref{fig:corefinement}, while in Fig.~\ref{fig:corefinement_remeshed}
the same mesh has been remeshed.
\begin{figure}
  \centering
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/heart_implicit.png}
    \caption{\label{fig:heart_tria}}
  \end{subfigure}\qquad
  \hfill
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/intersection_cube_sphere_mesh.png}
    \caption{\label{fig:corefinement}}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/cube_sphere_remeshed.png}
    \caption{ \label{fig:corefinement_remeshed}}
  \end{subfigure}
  \caption{\it (a) Triangulation created by filling a heart-shaped surface implicitly described by a function $f$. (b) Union of a cube with a sphere with badly shaped cells at the intersection. (c) Remeshed version of the same triangulation.}
\end{figure}

\texttt{CGALWrappers::compute\_quadrature\_on\_boolean\_operation()} returns a \texttt{Quadrature<3>} that allows exact integration of polynomials on polyhedral elements coming out of a \texttt{BooleanOperation} between \dealii cells.
The quadrature rule is built by meshing the polyhedral region with tetrahedra, computing on each tetrahedron a \texttt{QGaussSimplex<3>} quadrature rule by using \texttt{QSimplex<3>::\allowbreak{}compute\_affine\_transformation()}, and finally
collecting all of the rules together, giving a \texttt{Quadrature<3>} formula on the \emph{physical} element.

These utility functions will be the building blocks for functions in the \texttt{NonMatching} namespace that will, e.g.,  assemble coupling terms like $(u,v)_{\Omega}$, with $\Omega$ a domain immersed in a fixed background mesh $B$ and $u,v$ finite element functions on $V_h(B)$, as needed, e.g., in 
the context of CutFEM (see Section~\ref{sec:cut}) or Nitsche's method to weakly impose boundary conditions at an interface. The same applies to coupling terms of the form $(u,q)_{\Omega}$ in formulations using Lagrange multipliers, where now $q \in Q_h(\Omega)$, with $Q_h(\Omega)$ the space of the multiplier variable.
Note that the most relevant difference between this and the \texttt{QuadratureGenerator} in Section~\ref{sec:cut} is that the \texttt{Quadrature} objects are created directly from two overlapping grids, one
spanning over $B$ and the other one over $\Omega$, and not from a level set function.

@@

\begin{table}
  \caption{\it Timing of various particle operations for tutorial program \texttt{step-68} (particle advection in a 2D, Cartesian box) using 400,000 particles on a single process.}
  \label{tab:particle_timing}

  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
   Particle Operation & \dealii 9.3 & \dealii 9.4 & Speedup \\
   \hline
   Generation & 444 ms & 235 ms & 1.9$\times$ \\
   Iteration & 4.18 ms & 0.638 ms & 6.6$\times$ \\
   Advection & 37.8 ms & 33.9 ms & 1.15$\times$ \\
   Sorting & 21.9 ms & 9.27 ms & 2.4$\times$ \\
   \hline
  \end{tabular}
  \end{table}

@@

@@

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-81} was contributed by Manaswinee Bezbaruah (Texas A\&M
    University) and Matthias Maier (Texas A\&M University). It explains how
    to solve the complex-valued time-harmonic Maxwell's equations for an
    optical scattering problem.
  \item
    \texttt{step-82} was contributed by Andrea Bonito (Texas A\&M
    University) and Diane Guignard (University of Ottawa). It shows how
    \dealii can be used to implement the local discontinuous Galerkin
    (LDG) method for approximating the solution to the bi-Laplacian
    problem. The method is an alternative to the C0IP method used in
    \texttt{step-47}.
  \item
    \texttt{step-85} was contributed by Simon Sticko (Uppsala University).
    It shows how to use the new CutFEM infrastructure to solve a Poisson
    problem on a circular domain that is embedded in a Cartesian background
    mesh.
\end{itemize}

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
  \begin{itemize}[leftmargin=4mm]
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ArborX \cite{lebrun2020arborx}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item CGAL \cite{cgal}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries.

>>>>

\usepackage{booktabs}

@@

\dealii version 9.4.0 was released June 24, 2022.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.4. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Experimental integration of the Computational Geometry Algorithms Library (CGAL) (see Section~\ref{sec:cgalwrappers});
  \item Performance improvements in the particle infrastructure (see Section~\ref{sec:particles});
  \item Support for large MPI buffers and parallel I/O (see Section~\ref{sec:large-mpi});
  \item Improvements to unstructured communication (see Section~\ref{sec:CA});
  \item Three new tutorial programs and one new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class interpolates values defined on one
  triangulation onto a second potentially unrelated triangulation.
  By using this class, one can output the result obtained on an
  unstructured mesh on a structured one (which might facilitate a more
  memory-efficient storage format, for example if this second
  triangulation is a uniformly refined rectangle or box), or one can create a slice in 3D.
  \item The new member function \texttt{find\_point\_owner\_rank()} of
        \texttt{parallel\allowbreak ::distributed::\allowbreak Tri\allowbreak angulation} allows one to find the MPI
  ranks of cells containing specified points.
  It is communication-free and leverages the functionality of \pfrst (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. This information will
  enable efficient construction of the
  communication pattern used in the class \texttt{Utilities::\allowbreak MPI::\allowbreak RemotePointEvaluation}. Furthermore, this function could be used in the future to allow
  particle simulations in which particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction()}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description is applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \item A new DoF renumbering function \texttt{DoFRenumbering::support\_point\_wise()} which groups together
  shape functions by their support point. This functionality is useful in both developing nodal schemes since, e.g., the $x$, $y$, and $z$
  velocities at a point will be consecutive in the solution vector. It also improves interoperability with external libraries which expect
  data in this format.
  \item The \texttt{FEInterfaceValues} class, which computes common quantities at the interface of two cells, has been overhauled to make it
  more consistent with the rest of the library and use more intuitive names for functions. For example,
  \texttt{FEInterfaceValues::jump\_gradient()} is now \texttt{FEInterfaceValues::jump\_in\_shape\_gradients()}. Several new
  functions, such as \texttt{FEInterfaceValues::get\_jump\_in\_function\_values()}, have also been added.
  \item The\texttt{MeshWorker::ScratchData} and \texttt{MeshWorker::CopyData} have been made $hp$-compatible,
  and supports face integration where the integration rule and mapping differs on either side of an interface.
  The \texttt{MeshWorker::CopyData} class has also been made compatible with complex numbers.
  \item Vectors attached to \texttt{DataOut} do not need to be in ghosted state anymore. Internally, we create a copy of the vector with appropriate ghosting.
\end{itemize}
%
The changelog lists more than 100 other features and bugfixes.

@@

Specifically, the following are the key new classes and functions:
\begin{itemize}
  \item The \texttt{MeshClassifier} class identifies how the active cells and faces are located relative to the zero contour of the level set function, as illustrated in Figure~\ref{fig:location-to-level-set}. Its member function \texttt{location\_to\_level\_set()} takes a cell or face and
        returns an enum, \texttt{LocationToLevelSet}, with values \{\texttt{inside}, \texttt{outside}, \texttt{intersected}\}.
        This information is typically needed when choosing what element (e.g., \texttt{FE\_Q} or \texttt{FE\_Nothing}) and/or what quadrature (defined over the 
        complete cell or over a part---see below) a cell
        should use.

@@

The Computational Geometry Algorithms Library (CGAL, \url{https://www.cgal.org/}) is a widely used
library to describe geometries and meshes \cite{cgal}. \dealii now
has wrappers for CGAL classes and functions, provided in the new
namespace \texttt{CGALWrappers}: they implement functionality
spanning from mesh generation to boolean operations between
triangulations and cells. These wrappers are enabled only if \dealii
is compiled with \texttt{C++17}. \textit{Note: This feature is still experimental and
interfaces might change during the next release cycle.}

@@

A related function is
\texttt{GridGenerator::surface\_mesh\_to\_volumetric\_mesh()}, which
computes a tetrahedral volume mesh \texttt{Triangulation<3>}, based on a
given surface mesh \texttt{Triangulation<2,3>} that bounds
the three dimensional shape.

CGAL also provides Boolean operations on meshes: they can be accessed via 
the utility function
\texttt{CGALWrappers::\allowbreak{}compute\_boolean\_operation()}. The
available operations are \textit{co-refinement}, \textit{intersection},
\textit{union}, and \textit{difference}. Oftentimes, Boolean
operations and co-refinement around the intersection produces
badly shaped mesh cells. To overcome this issue, one can use \texttt{CGALWrappers::\allowbreak{}remesh\_surface()}.
A possible workflow to create a good-quality mesh of the union of a cube and
a sphere mesh is given in the following listing:
\begin{c++}
// 1) create deal.II triangulations, e.g., cube and sphere (not shown)  
Triangulation<spacedim> tria0, tria1;

@@

// 5) convert surface to volume mesh via surface_mesh_to_volumetric_mesh()
\end{c++}
The output of the Boolean operation is shown in Fig.~\ref{fig:corefinement};
Fig.~\ref{fig:corefinement_remeshed} shows the mesh after remeshing.
\begin{figure}
  \centering
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/heart_implicit.png}
    \caption{\label{fig:heart_tria}}
  \end{subfigure}\qquad
  \hfill
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/intersection_cube_sphere_mesh.png}
    \caption{\label{fig:corefinement}}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/cube_sphere_remeshed.png}
    \caption{ \label{fig:corefinement_remeshed}}
  \end{subfigure}
  \caption{\it (a) Triangulation created by filling a heart-shaped surface implicitly described by a function $f$. (b) Union of a cube with a sphere with badly shaped cells at the intersection. (c) Remeshed version of the same triangulation.}
\end{figure}

The function \texttt{CGALWrappers::compute\_quadrature\_on\_boolean\_operation()} returns a quadrature that allows exact integration of polynomials on polyhedral elements created by a \texttt{Boolean\allowbreak Operation} between \dealii cells.
The quadrature rule is built by 1) subdividing the polyhedral region in tetrahedra, 2) computing on each a \texttt{QGaussSimplex<3>} quadrature rule via \texttt{QSimplex<3>::\allowbreak{}compute\_affine\_transformation()}, and 3)
collecting all in a single \texttt{Quadrature<3>} object on the \emph{physical} cell.

The new utility functions will be the building blocks for functions in 
the \texttt{NonMatching} namespace in future releases. While our current 
CutFEM implementation (see Section~\ref{sec:cut}) relies on a level set description of the domain to determine
the boundary and the quadrature rules, one could do that also based on non-matching overlapping
grids~\cite{massing2013efficient}, for which the newly introduced, CGAL-based Boolean operations and 
quadrature-generation functionality might be helpful. We would like to point out
that the functionalities are not limited to CutFEM but are also applicable
for weakly imposing boundary conditions on the interface of an immersed boundary
using Nitsche's method and coupling terms using Lagrange multipliers.

%These utility functions will be the building blocks for functions in the \texttt{NonMatching} namespace that will, e.g.,  assemble coupling terms like $(u,v)_{\Omega}$, with $\Omega$ a domain immersed in a fixed background mesh $B$ and $u,v$ finite element functions on $V_h(B)$, as needed, e.g., in 
%the context of CutFEM (see Section~\ref{sec:cut}) or Nitsche's method to weakly impose boundary conditions at an interface. The same applies to coupling terms of the form $(u,q)_{\Omega}$ in formulations using Lagrange multipliers, where now $q \in Q_h(\Omega)$, with $Q_h(\Omega)$ the space of the multiplier variable.
%Note that the most relevant difference between this and the \texttt{QuadratureGenerator} in Section~\ref{sec:cut} is that the \texttt{Quadrature} objects are created directly from two overlapping grids, one
%spanning over $B$ and the other one over $\Omega$, and not from a level set function.

@@

\begin{table}
  \caption{\it Timing of various particle operations for tutorial program \texttt{step-68} (particle advection in a 2D, Cartesian box) using 400,000 particles on a single process.}
  \label{tab:particle_timing}
  \centering
  \begin{tabular}{lccc}
    \toprule
    Particle Operation & \dealii 9.3 & \dealii 9.4 & Speedup      \\[0.3em]
    Generation         & 444 ms      & 235 ms      & 1.9$\times$  \\
    Iteration          & 4.18 ms     & 0.638 ms    & 6.6$\times$  \\
    Advection          & 37.8 ms     & 33.9 ms     & 1.15$\times$ \\
    Sorting            & 21.9 ms     & 9.27 ms     & 2.4$\times$  \\
    \bottomrule
  \end{tabular}
  \end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for large MPI buffers and parallel I/O}
\label{sec:large-mpi}

   Sending large messages over MPI or reading and writing large buffers using MPI I/O,
   especially when dealing with small datatypes like \texttt{MPI\_CHAR},
   can often require processing more than $2^{31}$ objects at once. Prior
   to the recent MPI-4 standard, which introduced a new set of \texttt{MPI\_*\_c()} functions, all MPI functions expected the ``count''
   to be a signed integer. This limits the number of objects to $2^{31}$,
   i.e., writing of up to 2 GB at once if the datatype is \texttt{MPI\_CHAR}.

   Several places in the library could run into the issue mentioned above,
   for example when producing large graphical output (per rank), large
   checkpointing (per rank), or when broadcasting large datasets for lookup tables.

   With this release we introduce a new module \texttt{Utilities::MPI::LargeCount} which enables sending and receiving MPI messages and I/O containing more than $2^{31}$ objects by implementing
   the before-mentioned \texttt{MPI\_*\_c()} functions, i.e., \texttt{MPI\_Bcast\_c()}, using MPI-3 features if necessary. The
   solution is based on custom datatypes as described in~\ref{hammond2014int_max}.

   This functionality is now used in all places in the library, where
   large counts might be necessary (\texttt{DataOut::write\_vtu\_in\_parallel()} for graphical output, checkpointing of \texttt{Triangulation} objects, etc.).
   %
   While implementing these changes we also worked on the following:
   \begin{itemize}
    \item Testing of large I/O with large chunks per MPI rank (>2 GB) and
    large total sizes (4 GB +). Several instances of 32 bit datatypes for
    offsets were changed to 64 bit to correctly support files larger
    than 4 GB (HDF5 output, VTU output, checkpointing).
    \item Performance testing of MPI I/O routines used for parallel VTU output with large performance improvements by switching from a shared
    file pointer to individual file pointers, see Table~\ref{tab:mpi-io}.
   \end{itemize}

\begin{table}
  \caption{\it Performance comparison of writing large VTU graphical output using MPI I/O on
  TACC Frontera /scratch1/ with 16 file servers (``OSTs'') and a theoretical peak performance of 50 GB/s. The ROMIO version used enforces sequential writes when using \texttt{MPI\_File\_write\_ordered()}.}
  \label{tab:mpi-io}

  \begin{tabular}{llcc}
    \toprule
    Version       & MPI routine used                     & 1 file, striping 16 & 16 files, no striping \\[0.3em]
    \dealii{} 9.3 & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s               \\
    \dealii{} 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s               \\
    \bottomrule
\end{tabular}

  \end{table}

@@

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-81} was contributed by Manaswinee Bezbaruah (Texas A\&M
    University) and Matthias Maier (Texas A\&M University). It explains how
    to solve the complex-valued time-harmonic Maxwell equations for an
    optical scattering problem.
  \item
    \texttt{step-82} was contributed by Andrea Bonito (Texas A\&M
    University) and Diane Guignard (University of Ottawa). It shows how
    \dealii can be used to implement the local discontinuous Galerkin
    (LDG) method for approximating the solution to the bi-Laplacian
    problem. The method is an alternative to the C0IP method used in
    \texttt{step-47}.
  \item
    \texttt{step-85} was contributed by Simon Sticko (Uppsala University).
    It shows how to use the new CutFEM infrastructure to solve a Poisson
    problem on a circular domain that is embedded in a Cartesian background
    mesh.
\end{itemize}

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
  \begin{itemize}[leftmargin=4mm]
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ArborX \cite{lebrun2020arborx}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item CGAL \cite{cgal}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Boost \cite{boost-web-page}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{Galassi2009,gsl-web-page}
    \item Ginkgo \cite{Anzt2022,ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,MUMPS:3,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est,burstedde2020parallel}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries.
